Visualization of Fractional Integrals

### 2019-03-04 fractional/CMJ style files/article-template.tex
added first equations --- needs to be fleshed out dramatically

\title{CMJ Article Title}
\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
%\author{ }

@@

>>>>

\title{Visualization of Fractional Integrals}
\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
%\author{ }

@@

\section{xxx}
The fractional integral is defined as (need to be more explicit here). Need to add how it has come about... Start with a single integral, expand to the general case and then 
to a general $\alpha$. 
\begin{equation}
\frac{1}{\Gamma(\alpha)}\int_{0}^{t}f(\tau)(t-\tau)^{\alpha-1}~d\tau
\end{equation}

Podlubny showed that the fractional integral can be rewritten as a Riemann-Stieltjes integral:
\begin{equation}
\label{eq:rs}
\int_0^{\tau} f(\tau)~dg_t(\tau),
\end{equation}
with 
\begin{equation}
g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
\end{equation}

We can now transform Equation~\ref{eq:rs} into an equivalent Cavalieri integral:
\begin{equation}
\label{eq:cav}
\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau, 
\end{equation}
with
\begin{equation}
a_t^{\alpha}(y) = f^{-1}(y) - \frac{t^{\alpha}-(t-f^{-1}(y))^{\alpha}}{\Gamma(\alpha+1)}
\end{equation}

Since Equation~\ref{eq:cav} is a Cavalieri integral, it has a clear geometric interpretation. The integral in eq xxx can be interpreted as the sum
